---
title: "Lab 10"
author: "Katie Pietrucha"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(usethis)
library(beepr)
library(praise)
library(cowsay)
library(sf)
library(paletteer)
```

## beepr::beep()

Makes a noise! Could be helpful to let you know when code is done running, if it's going to take hours...)

Use `beep()` to give yourself an audio alert.

## for loop + beep

```{r, eval = FALSE}
for (i in rev(seq(1:9999))) {
  print(paste(i, "bottles of beer on the wall"))
}

beep(4)
```

## praise is nice

```{r}
praise("${EXCLAMATION}!!! This code works ${adverb_manner}!")

praise("Holy ${creating}, Batman - this code works ${ADVERB_MANNER}!")
```

## cowsay::say to have characters say something

```{r}
say("don't eat me!", by = "pig")
```

## usethis for everything

R Project first, then git & GitHub repo.

- usethis::use_git()
- usethis::use_github()

## paletteer: aggregated color palettes

```{r}
storms %>%
  group_by(name) %>%
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>%
  slice_min(n = 10, min_pressure) %>%
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("dutchmasters::milkmaid")
```

## Map of Jornada LTER Vegetation

```{r}
jornada_veg <- read_sf("doc.kml") %>%
  select(Name) %>%
  clean_names()

ggplot() +
  geom_sf(data = jornada_veg, aes(fill = name), color = NA) +
  theme_bw() +
  scale_fill_paletteer_d("ggthemes::manyeys") +
  labs(title = "Jornada Basin LTER Vegetation")

# Update this map:
# Each vegetation type has a different fill color
# Update theme
# Customize the color palette

# Save as image
ggsave(filename = "my_awesome_jornada_map.png", width = 8, height = 5)
```

